To boldly go where no science...

### 2016-05-02 nyu-data-science-reproducibility-16/be-bold.Rmd
revise be-bold

## TL;DR

@@

- Replications can fail due to methdological differences
- Methods sections don't always report essential details
- **Video captures and preserves it**

@@

## [Databrary.org](http://databrary.org)

- Digital data library specialized for research video
- Video/audio + participant/context metadata
- Restricted access for research/educational use
- Policy framework for sharing identifiable data
- Developmental science focus, but not exclusive

<iframe src="http://databrary.org" width=640px height=400px>
</iframe>

@@

- Policies for sharing identifiable video data
- Tools for coding video
- Tools for "active curation"" during data collection

@@

- Raw research video must be coded
- [Datavyu.org](http://datavyu.org) = free, [open source](https://github.com/databrary/datavyu) coding tool
- Add codes, annotations time-locked to video segments
- Ruby API for [scripting](https://github.com/databrary/Datavyu-Example-Scripts) reproducible workflows

@@

- Organize, share, standardized participant metadata
- Sharing based on 
    + user access level
    + participant permission

@@

- Video uniquely captures complexity & richness of behavior
- Video captures vital methodological details in behavioral research
- Identifiable video (and other data) can be shared
- Video data sharing essential for a reproducible behavioral science

## Join us!

<iframe src="https://databrary.org/about/jobs.html" width=640px height=400px>
</iframe>

>>>>

## TL; DR

@@

- Replications can fail due to methodological differences
- Methods sections don't always report essential details
- **Video captures and preserves it**

@@

## [Databrary.org](http://databrary.org) makes this possible

- Digital data library specialized for research video
- Video/audio + participant/context metadata
- Share displays, materials, text-based data files
- Restricted access for research/educational use
- Policy framework for sharing identifiable data
- Developmental focus, but not exclusive

@@

- Policies for sharing identifiable video data
- Tools for reproducibly coding video
- Tools for "active curation" == during data collection

@@

- Raw research video must be coded
- [Datavyu](http://datavyu.org) a free, [open source](https://github.com/databrary/datavyu) coding tool
- Add codes, annotations time-locked to video segments
- Turn behavior into quantifiable data
- Ruby API for [scripting](https://github.com/databrary/Datavyu-Example-Scripts) reproducible workflows

@@

- After-the-fact curation burdensome
- Databrary organizes, shares, standardized participant metadata
- Sharing based on
    + user access level
    + participant permission

@@

- Video uniquely captures complexity & richness of behavior
- Video captures vital methodological details
- Identifiable video (and other data) can be shared
- Preparing to share reduces the burden
- Video data sharing essential for a reproducible behavioral science
